In this chapter we will on the one hand discuss, what the overall aim of theproject is, and what the objectives are, which we want to achieve – either onthe way through the project or in its end. Furthermore we will forecast, whatour expected outcome of the project is and what the reasons for this forecastare.\section{Aim}The aim of the project is to create a system which helps the user to bring outhis car from a parking position in the simplest, yet most convenient andreliable way possible.\section{Objectives}The project's objectives are:\begin{itemize}  \item{Satisfaction of the customer \newline	We measure our success rate with the satisfaction level of our customers.	} 	\item {Satisfaction of the end consumer \newline	Since this is a system, our customer wants to make to provide support for his	customers, his own satisfaction, and thus our success, will highly depend on	this factor. We want to make his life easier, without asking too much of	technical knowledge or making things so complicated to use, that he decides to	do his actions without the help of our system. }	\item{Creation of a satisfying hardware analysis \newline Since the system is	supposed to use third party hardware for significant parts of the	functionality, it is an objective to create a good analysis on the state of art	of the needed variety of sensors.}	\item {Create a System that is significant on the market \newline We want to	create a system which other systems get compared to, when it comes to measuring	the quality.}\end{itemize}\section{Expected Outcome}The expected outcome of this project is, due to the lack of time and hardware:\begin{itemize}  \item A representative market analysis of current competition systems with the contrast to our product  \item A representative market analysis on the needed hardware pieces for oursystem   \item A solid and justified concept for a solution  \item A proof of concept\end{itemize}